\textbf{\sffamily\Huge \ShortTitle}\\ {\textbf{\sffamily\Large \FullTitle}} \vspace{1cm}

### 2012-12-06 paper/mswp2012-proposal.tex
gantt

\usepackage{graphicx}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% \usepackage{mathptmx} % Times New Roman

@@

\note{
\begin{itemize}
\item {\em Length: 1-2 pages}
\item Realistic estimation of schedule based on workpackages.
\item Including milestones (not only when but also what is to be achieved for each milestone).
\item Generation of a Gantt chart. (Including phases, milestones, buffer times, critical areas, etc.)
\end{itemize}
}

>>>>

\usepackage{graphicx}
\usepackage{natbib}
\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{color}
\usepackage{subfigure}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
% \usepackage{mathptmx} % Times New Roman

@@

\begin{figure}\centering
\subfigure[part 2]{\includegraphics[width=5cm]{images/gantt/Gantt_part12.png}}
\subfigure[part 1]{\includegraphics[width=5cm]{images/gantt/Gantt_part1.png}}
\caption{Gantt Chart}
\end{figure}

\begin{figure}\centering
\subfigure[part 4]{\includegraphics[width=5cm]{images/gantt/Gantt_part22.png}}
\subfigure[part 3]{\includegraphics[width=5cm]{images/gantt/Gantt_part2.png}}
\caption{Gantt Chart}
\end{figure}

%\note{
%\begin{itemize}
%\item {\em Length: 1-2 pages}
%\item Realistic estimation of schedule based on workpackages.
%\item Including milestones (not only when but also what is to be achieved for each milestone).
%\item Generation of a Gantt chart. (Including phases, milestones, buffer times, critical areas, etc.)
%\end{itemize}
%}

%\begin{figure}[h]
%\centering
%\begin{minipage}{.4\textwidth}
%\includegraphics[width=6cm]{images/gantt/Gantt_part1.png}
%\caption{Gantt part 1}
%\label{fig:ganttpart1}
%\end{minipage}
%\begin{minipage}{.4\textwidth}
%\includegraphics[width=6cm]{images/gantt/Gantt_part2.png}
%\caption{Gantt part 2}
%\label{fig:ganttpart2}
%\end{minipage}
%\end{figure}
